---
title: "NL Data cleaning"
output: html_notebook
---

```{r}
library(tidyverse)
```

Read in data


```{r}
NL_master <- read_csv("~/Box/Dilsher/Andrew/Flow_project/Data Files/NL_master.csv")
dta<-NL_master
```

##### Cleaning steps 
1. Add '_' to all empty spaces in variable names 
2. Remove the % sign from the expression variables and convert to numeric
3. Keep only those samples that were run on baseline.
4. Remove ARD and AD samples - **Tomo, what are these?**


**1, 2 and 3**
```{r}
tidy.name.vector <- make.names(names(dta), unique=TRUE)
names(dta)<-tidy.name.vector



dta<-dta%>%
  mutate(visit=sapply(str_split(dta$Patient.visit.ID,"-"),"[",2))%>%
  filter(visit=="1" |is.na(visit))%>% ## either baseline which is 1 or NA, which indicates baseline 
  mutate_all(funs(gsub("%","",.)))%>%
  mutate_at(.,vars(CD107a:TNF),funs(as.numeric))%>%
  mutate(ID=gsub( "_.*$", "",ID_stim)) %>%   # Create a sample ID because Tomo made a typo in his ID variable 
  filter(ID!="ARD")%>%
  filter(ID!="ArD")%>%
  filter(ID!="AD")
  
```

```{r}
dta%>%
  count(Stim)

```

#### Data processing 
We need to calculate the fold change and/or the baseline(nil), values according to the below - from Andrew's email on January 25, 2019

IL-13: both upregulation and baseline (I suspect upreg will be better)
IFNg: upregulation
PD1: baseline
IL4: both baseline and upregulation (I suspect baseline will be more informative)
TNF: upregulation
Tbet: both baseline and upregulation
Ki67: both
Perforin: both
IL1-: upregulation
CD107a: upregulation
GATA3: both
CD107a: upregulation


**Calculate the Fold change for all as compared to baseline**
```{r}
dta<- dta%>%
    mutate(nil=ifelse(grepl("nil",Stim,ignore.case = TRUE),"Yes","No"))%>%
     group_by(ID)%>%
        arrange(desc(nil),.by_group=TRUE)%>%
          mutate_at(.funs = funs(fc=./.[1]),vars(CD107a:TNF))%>%
            ungroup()
```

**Create a fold change dataframe and a baseline dataframe**
```{r}
fc_data<-dta%>%
  select(c(ID,Stim,contains("fc")))

baseline_data<-dta%>%
  select(c(ID,Stim,CD107a:TNF))
```

```{r}
save(fc_data,file="~/Box/Dilsher/Andrew/Flow_project/Data Files/NL_fc_data.rda")
save(baseline_data,file="~/Box/Dilsher/Andrew/Flow_project/Data Files/NL_baseline_data.rda")
save(dta,file="~/Box/Dilsher/Andrew/Flow_project/Data Files/NL_cleaned_data.rda")


```






