---
title: "NL Plotting"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
*Import Libraries* 
```{r include=FALSE}
library(tidyverse)
library(corrplot)
```
*Load the data* 
```{r,include=FALSE}
load(file="~/Box/Dilsher/Andrew/Flow_project/Data Files/NL_fc_data.rda")
load(file="~/Box/Dilsher/Andrew/Flow_project/Data Files/NL_baseline_data.rda")
load(file="~/Box/Dilsher/Andrew/Flow_project/Data Files/NL_cleaned_data.rda")

```




### Looking at the *upregulation* for all the 4 stimulus's - BCG, HIV, SEB and E/C 
For all the expression variables, look at the correlation for the 4 stimulus where for each stimulus, the expression is the fold change from the `nil sample`



```{r,include=FALSE}
#Create separate fold change data frames 

nested_fc<-fc_data%>%
  select(-ID)%>%
  group_by(Stim)%>%
  nest()%>%
  filter(Stim=="BCG"|Stim=="HIV"|Stim=="SEB" |Stim=="E/C")
nested_fc[[1]] # get the names 
bcg_fc<-nested_fc[[2]][[1]]
hiv_fc<-nested_fc[[2]][[2]]
seb_fc<-nested_fc[[2]][[3]]
ec_fc<-nested_fc[[2]][[4]]
```

**Create a plotting funtion**
```{r,include=FALSE}
dd_correlation_plots<-function(df){
  ## The data frame df should be a numeric df with the variables listed and the rows are simply the rownames ##
  c<-cor(df,use="pairwise.complete.obs",method = "spearman")
  p<-cor.mtest(df,method="spearman",continuity=TRUE)[[1]]
  p_adj<-p.adjust(p,method = "BH") ### BH correction multiple testing 
  p_adj_mat<-matrix(p_adj,nrow = ncol(df),ncol=ncol(df)) ## convert into matrix 
  rownames(p_adj_mat)<-rownames(c) ## 
  colnames(p_adj_mat)<-colnames(c)
  ## clustering
  #dd<-as.dist((1-abs(c)))
  
  #dir<-getwd()
  #dir.create(getwd)
  col1 <- colorRampPalette(c("#7F0000", "red", "#FF7F00", "green", "white",
                             "cyan", "#007FFF", "blue", "#00007F"))
  #dir<-"/Users/dilsherdhillon/Box/Dilsher/Andrew/Flow project/Andrew_Flow/Outputs/CD4_Flow"
  #dir.create(dir)
  #pdf(file.path(dir,paste0(deparse(substitute(df)),".pdf")))
  #par(mfrow=c(2,2))
  corrplot(c, type = "upper",method="number",col=col1(20),title=paste0(toupper(deparse(substitute(df))),"   Stimulus Spearman Correlation"),mar=c(0,0,1,0),number.cex = .7)
  
  corrplot(p_adj_mat,type="upper",method="number",cl.lim = c(0, 1),col=col1(20),title=paste0(toupper(deparse(substitute(df))),"   BH Adjusted p-values"),mar=c(0,0,1,0),number.cex = .7)
  #plot(hclust(dd,method = "ward.D"),main="Heirarchial Clustering")
  #title(paste0(toupper(deparse(substitute(df)))," Stimulus Correlation"), line = -21, outer = TRUE)
  #graphics.off()
  rm(c,p,p_adj,p_adj_mat,dd,col1)
}
```



**Correlation plots for upregulation** 
```{r echo=FALSE, message=FALSE, warning=FALSE}
dd_correlation_plots(bcg_fc)
dd_correlation_plots(hiv_fc)
dd_correlation_plots(seb_fc)
dd_correlation_plots(ec_fc)
```


\pagebreak


### Looking at only the *baseline* expression 
For all the expression variables, look at the correlation for the 4 stimulus where for each stimulus, the expression is the baseline expression.

```{r include=FALSE}
nested_baseline<-baseline_data%>%
  select(-ID)%>%
  group_by(Stim)%>%
  nest()%>%
  filter(Stim=="BCG"|Stim=="HIV"|Stim=="SEB" |Stim=="E/C")
nested_baseline[[1]] # get the names 
bcg_baseline<-nested_baseline[[2]][[1]]
hiv_baseline<-nested_baseline[[2]][[2]]
seb_baseline<-nested_baseline[[2]][[3]]
ec_baseline<-nested_baseline[[2]][[4]]

```


**Correlation plots for baseline** 

```{r echo=FALSE, message=FALSE, warning=FALSE}
dd_correlation_plots(bcg_baseline)
dd_correlation_plots(hiv_baseline)
dd_correlation_plots(seb_baseline)
dd_correlation_plots(ec_baseline)
```



